### 2017-07-09 README.Rmd
update with one prop

One categorical (2 level) variable
```
mtcars %>%
  select(am) %>%
  hypothesize(null = "point", p = .25) %>% 
  generate(reps = 100, type = "simulate") %>% 
  calculate(stat = "prop") #
```

Two categorical (2 level) variables

- Implemented

@@

One categorical (>2 level) - GoF
```
mtcars %>%
  select(cyl) %>%
  hypothesize(null = "point", p1 = .25, p2 = .25, p3 = .50) %>% # call levels() to find order of p's
  generate(reps = 100, type = "simulate") %>%
  calculate(stat = "chisq")
```

Two categorical (>2 level) variables
```
mtcars %>%
  select(cyl, am) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "chisq")
```

@@

- Implemented

@@

One numerical one categorical (>2 levels) -  ANOVA
```
mtcars %>%
  select(mpg, cyl) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "F")
```

Two numerical vars - SLR
```
mtcars %>%
  select(mpg, hp) %>%
  hypothesize(null = "independence") %>% # or "slope = 0"
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "lm(mpg ~ hp)")
```

>>>>

One categorical (2 level) variable

```
mtcars %>%
  select(am) %>%
  hypothesize(null = "point", p = c("1" = .25)) %>% 
  generate(reps = 100, type = "simulate") %>% 
  calculate(stat = "prop") #
```

Two categorical (2 level) variables (not yet implemented)

@@

One categorical (>2 level) - GoF  (not yet implemented)
```
mtcars %>%
  select(cyl) %>%
  hypothesize(null = "point", p = c("4" = .5, "6" = .25, "8" = .25)) %>% # call levels() to find order of p's
  generate(reps = 100, type = "simulate") %>%
  calculate(stat = "chisq")
```

Two categorical (>2 level) variables  (not yet implemented)
```
mtcars %>%
  select(cyl, am) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "chisq")
```

@@

@@

One numerical one categorical (>2 levels) -  ANOVA  (not yet implemented)

```
mtcars %>%
  select(mpg, cyl) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "F")
```

Two numerical vars - SLR  (not yet implemented)
```
mtcars %>%
  select(mpg, hp) %>%
  hypothesize(null = "independence") %>% # or "slope = 0"
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "lm(mpg ~ hp)")
```
